---
output: github_document
---

[![Travis build status](https://travis-ci.org/dirkschumacher/anthro.svg?branch=master)](https://travis-ci.org/dirkschumacher/anthro)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/dirkschumacher/anthro?branch=master&svg=true)](https://ci.appveyor.com/project/dirkschumacher/anthro)
[![Coverage status](https://codecov.io/gh/dirkschumacher/anthro/branch/master/graph/badge.svg)](https://codecov.io/github/dirkschumacher/anthro?branch=master)
[![CRAN status](https://www.r-pkg.org/badges/version/anthro)](https://cran.r-project.org/package=anthro)
[![lifecycle](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://www.tidyverse.org/lifecycle/#stable)

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Anthro

The `anthro` package allows you to perform comprehensive analysis of anthropometric survey data based on the method developed by the Department of Nutrition for Health and Development at the World Health Organization.


## Installation

Currenlty only available from Github.

```{r, eval=FALSE}
remotes::install_github("dirkschumacher/anthro")
```


## Examples
```{r, echo=TRUE}
library(anthro)
```

### Z-Score

This function calculates z-scores for the eight anthropometric indicators, weight-for- age, length/height-for-age, weight-for-length/height, body mass index (BMI)-for-age, head circumference-for-age, arm circumference-for-age, triceps skinfold-for-age and subscapular skinfold-for-age based on the WHO Child Growth Standards.

```{r}
anthro_zscores(sex = c(1, 2, 1, 1),
               age = c(1001, 1000, 1010, 1000),
               weight = c(18, 15, 10, 15),
               lenhei = c(120, 80, 100, 100))
```

The returned value is a `data.frame` that can further be processed or saved as a `.csv` file as in the original function.

You can also use the function with a given dataset with `with`

```{r, eval = FALSE}
your_data_set <- read.csv("my_survey.csv")
with(your_data_set, 
     anthro_zscores(sex = sex, age = age_in_days, 
                    weight = weight, lenhei = lenhei))
```

To look at all parameters, type `?anthro_zscores`.

### Prevalence

The prevalence estimates are similiar to `anthro_zscores`: again they take vectors instead of a data frame and column names for the aforementioned reasons.

```{r}
anthro_prevalence(sex = c(1, 2, 2, 1),
                  age = c(1001, 1000, 1010, 1000),
                  weight = c(18, 15, 10, 15),
                  lenhei = c(100, 80, 100, 100))[, 1:5]
```

Using the function `with` it is easy to apply `anthro_prevalence` to a full dataset.

To look at all parameters, type `?anthro_prevalence`.
